### 2018-02-12 Writing/Thesis/content/chapter-approach.tex

META FEATURES USED!

for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before

>>>>

\subsection{Classifiers}

\subsection{Regression and Preference Learning}

\subsection{Meta Features}
META FEATURES USED! \cite{OpenML2013}

\subsection{Other Used Implementations}
for mann-whitney U apache commons implementation used with ties averaged and NaNs removed before analysis
apache commons implementation for Kendall Rank correlation as well
JAICore implementation for stratified split of data set

### 2018-02-12 Writing/Thesis/content/chapter-conclusion.tex

% Summary of findings and limitations: what has been covered
- Results -

@@

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression based approach using random forests, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Different sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features.

@@

% Auto fitting
Depending on the fact whether one is willing to trade-off longer build and prediction times, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}.

>>>>

% Summary of findings and limitations: what has been covered LIMITATION: SMALL DATA SETS ESP!!
The evaluation showed a significant advantage regarding the Kendall rank correlation for all tested methods in comparison to the best algorithm baseline, except instance based label ranking in the standard configuration and label ranking by pairwise comparison for the full meta data. However, regarding the practically possibly more important measure of best three loss, only the three regression based variants with linear regression, M5P and random forest as the regression learners can hold a significant advantage. When evaluating best three loss on reduced meta data that does not incorporate probing, although the evaluated data indicates a slight advantage of those same regression models over the baseline still, it is not statistically significant anymore. Furthermore, some label ranking methods even show a significant disadvantage in comparison to the baseline for the best three loss and loss for both evaluation on the full and reduced meta data. Thus it can be included that a regression based approach seems to be generally more promising than the preference based approach, but is not better than the baseline regarding the best three loss when evalluated on the selected meta data without probing.

One of the main limitations of the findings in this thesis is that the data sets used in the evaluation process where not very large, being limited to a maximum of 100 features and 1000 instances. Often, data sets can get much larger and the question whether this ranking approach would then still pose an efficient and, maybe even more importantly accurate enough solution for predicting classifiers remains.

@@

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression based approach using random forests, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding best three loss when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump with two folds, RandomTree with a depth of two with two folds, REPTree with a depth of two and two folds, and J48.0001 with two folds, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation times for the meta features in the mean, which seems to be reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

@@

% Auto fitting
Depending on the fact whether one is willing to trade-off longer build and prediction times, it would also be possible to fit more sophisticated regression models for the regression based approach. This could include feature pre-processing, automating the choice of regression algorithm with one of the available tools \cite{thornton2013auto} \cite{feurer2015efficient}, or even using a whole pipeline prediction tool \cite{wever2017automatic} \cite{DBLP:conf/eurogp/SaPOP17}. Furthermore, the building and predictions for the regression models could be parallelized and evaluated on a cluster to simulate and test  the usage of the ranking tool in a productive environment.

### 2018-02-12 Writing/Thesis/content/chapter-evaluation.tex

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}. These include the Kendall rank correlation coefficient, loss and best three loss. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% Which meta features
As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used. Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew. Meta features where calculated with the help of an implementation provided by OpenML .Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.

@@

In the results mainly as so many data sets only taked about mean values but the full results with related to the specific data set id are included in supplementary material.

% Results of Base Algorithms and full meta features
% - scatter plot dataset -> best preferenceRanker, best regressionRanker, bestAlgorithmbaseline each Kendall

% Results include the 4 evals on all sets, how long predictions took. Meta feature calc times sperately, but may give avg of comp+predict time each time meta feature values table in appendix with mean,min,max stdev

% When removing probing

% When removing expensive meta features

% Results of optimized variants? full / no probing / no expensive

% Insights about classifiers: place best ranking, min, max rank (optional) for each classif?

@@

@@

\input{tables/metaFeatureTimes}
\ref{tab:metaFeatureTimes}

@@

\addtocounter{footnote}{-2}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young}
\stepcounter{footnote}\footnotetext{Rankaggregation: Kemeny-Young, Baselearner KNN with n=$\sqrt{\text{number of instances}}$}

\tikzsetnextfilename{LossGraphics}
\pgfplotsset{width=\textwidth}
\begin{tikzpicture}
\begin{axis}
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=Loss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=Loss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
\legend{IB Label KY, Best Algorithm}
\end{axis}
\end{tikzpicture}

\tikzsetnextfilename{BestThreeLossGraphics}
\pgfplotsset{width=\textwidth}
\begin{tikzpicture}
\begin{axis}
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/InstanceBasedLabelRankingKemenyYoung_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,red] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
%\addplot [mark=none,red,samples=2,domain=0:450]{6.48};
%\addplot [mark=none,black,samples=2,domain=0:450]{5.44};
\legend{IB Label KY, Best Algorithm}
\end{axis}
\end{tikzpicture}

\subsection{Build and Prediction Times}

\input{tables/times}
\ref{tab:times}
%TODO add values for pairwise comparision in this table

@@

\input{tables/rootMeanSquareError}
\ref{tab:rootMeanSquareError}

\input{tables/bestAlgorithmRanking}
\ref{tab:bestAlgorithmRanking}

>>>>

% Evaluation Measures used & computed
As rankings returned by this oracle represent the ideal solution, the predicted rankings are compared with them through the measures presented in chapter \ref{chapter:fundamentals}. These include the Kendall rank correlation coefficient, loss and best three loss. For all three measures, it is computed if any advantages or disadvantages one solutions has is significant, by means of the Mann-Whitney U. The regression based rankers pose a special case: internally, they predict a performance value for each classifier, which therefore can be compared to the actual performance values to show how well they are predicted. This is done by computing the root mean square error between the predicted and actual performance values. In summary, it is desirable for the rankers to come as close as possible to the correct ranking, which is reflected by a high rank correlation and a low loss and root mean square error.

@@

% Which meta features
As for the meta features, all meta features discussed in chapter \ref{sec:approach} where used. Initially, it was intended to download the computed meta features from OpenML, but since missing values for meta features ranged from roughly 25\% up to 89\% (except for a few simple meta features which were included for all data sets) it was decided to compute them anew. Meta features where calculated with the help of an implementation provided by OpenML \cite{openMLEvaluationEngine}.Two data sets, one including the downloaded meta features (for all 812 data sets) and one including the computed meta features (for the reduced set of 448 data sets) are thus included in the supplementary material.

@@

In the following subsections, results of the evaluation are discussed in detail. First, the quality of the predictions of the rankers is examined. Then, the times required for building the rankers and for predictions made as well as for the calculation of the meta features is reviewed. Last, additional insights gathered during the evaluation are pointed out.

@@

- on the full meta data set, all approaches except for instance based with kemeny young and pairwise comparison

@@

@@

\tikzsetnextfilename{LossGraphics}
\begin{figure}
\pgfplotsset{width=.5\textwidth}
\begin{tikzpicture}
\begin{axis}[ylabel={BestThreeLoss}, xlabel={Data Set}]
\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
\end{axis}
\end{tikzpicture}%
~%
%
%\begin{tikzpicture}
%\begin{axis}[ymin=-5, ymax=25,ylabel={BestThreeLoss}, xlabel={Data Set}]
%\addplot [mark=*,only marks,mark size=1pt] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/BestAlgorithmRanker_metaData_small_allPerformanceValues.csv};
%\addplot [mark=*,only marks,mark size=1pt,uniaccentblue] table [x=ID,y=BestThreeLoss,col sep=semicolon] {data/RandomForestRanker_metaData_small_allPerformanceValues.csv};
%\addplot [very thick,mark=none,black,samples=2,domain=0:450]{2.440};
%\addplot [very thick,mark=none,uniaccentblue,samples=2,domain=0:450]{1.308};
%\legend{BestAlgorithm, RandomForest, BestAlgorithm (mean), RandomForest (mean)}
%\end{axis}
%\end{tikzpicture}
\caption{The Best Three Loss for the Best Algorithm Baseline and the Random Forest Ranker (Full Meta Data)}
\label{fig:lossGraphics}
\end{figure}

\subsection{Computation Times}

Because the ranking itself is implemented as a means of speeding up the process of algorithm selection, the time it takes to rank is not negligible. The full results of how long it takes to build the respective ranking models and how much time they need for predictions can be taken from Table \ref{tab:times}. Results are rounded to the full millisecond, as due to the times being measured with a stop watch in the code, more accurate measurements are not possible anyways. The times for building the regression rankers are not surprising; the regression models take far more time to be built than most of the label ranking methods, most likely due to the fact the regression based rankers have to train 22 regression models in order to be trained themselves. However, it is notable that while the ranking by Pairwise Comparison was not among the best solutions concerning the accuracy of the results, it is the ranker with the highest mean build time for full meta data, and second highest for a reduced meta data set, whereas in other cases the high quality of results is correlated with a high time invested in the building of the ranker likewise. The Random Forest ranker, for example, is the ranker with the highest build time, and also with the rankings of the generally highest quality. But the most important fact to be taken away from Table \ref{tab:times} is that the prediction times for all rankers are short enough to be negligible, with the mean prediction time never being higher than five milliseconds and the maximum never exceeding 50 milliseconds. Furthermore, while the build times are higher, these are not as important due to the fact that each model only needs to be trained once. Although in a real-world scenario, calculation times for meta features also have to be taken into account when ranking, which therefore will be discussed in the following paragraph.

\input{tables/times}

Table \ref{tab:metaFeatureTimes} shows the times required For the full meta features, on average approximately 135 milliseconds would be added to the prediction times 3 milliseconds whithout probing

\input{tables/metaFeatureTimes}

@@

Further insights to be noted are the accuracy of predictions of performance values for classifiers by the regression models, and the static ranking constructed by the best algorithm baseline. The accuracy of the predictions achieved by the regression based rankers are depicted in Table \ref{tab:rootMeanSquareError}, for full and reduced meta data respectively. The first thing that attracts attention in this table is the absurdly high values for Linear Regression and M5P, however, these are all caused by the very high maximum value on one data set with id 685. If these extreme maxima remain out of consideration for Linear Regression and M5P (the other algorithms do not have this problem) more reasonable values are obtained. For M5P, on the full meta data the new maximum is 311.526, mean 8.127 and standard deviation 18.407; on the reduced meta data it is a maximum of 474.692, mean 15.444 and standard deviation 27.433. For Linear Regression, on the full meta data the new maximum is 142.996, mean 9.281 and standard deviation 8.438; on the reduced meta data it is a maximum of 131.456, mean 14.351 and standard deviation 10.299. However, these values are still worse than the ones obtained for the Random Forest and REPTree variants. It comes as little surprise that the Random Forest Ranker also delivers the most accurate results for performance estimates, but as these best values are more than 6\% off on average for the full meta data and even more than 10\% off on average for the reduced meta data, it is questionable whether these prediction can be useful.

\input{tables/rootMeanSquareError}

The second interesting thing to consider is the ranking which is created by the best algorithm baseline. This ranking constitutes meta-knowledge about the learning process itself in that it shows which algorithms are generally a good choice for many data sets. This ranking is depicted in Table \ref{tab:bestAlgorithmRanking}. The table is to be read top to bottom; of the 22 algorithms, the algorithm in the ith row is placed first on most data sets when compared to the next 22-i algorithms. The associated number represents the number of data sets on which the algorithm was placed first. It is, however, not a particularly surprising result, as for example the placement of Random Forest as the first algorithm was to be expected. Random Forest is a learning algorithm that is known to often deliver good performances, which was proven again in the results discussed previously - out of the reviewed ranking approaches, Random Forest was the best choice.

\input{tables/bestAlgorithmRanking}

### 2018-02-12 Writing/Thesis/content/chapter-related-work.tex

\section{Predicting Rankings}
%% Ranking
% Incorporating times
In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifier \cite{DBLP:journals/ml/AbdulrahmanBRV18}. They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches.

@@

% Active testing A3R

% Introduce loss curves and how the measure influences them

>>>>

\section{Predicting Rankings}
%% Ranking
% Incorporating times
In contrast to ranking solely based on classifier performances, \citeauthor{DBLP:journals/ml/AbdulrahmanBRV18} investigated an approach to extend existing ranking methods by incorporating the time needed for the evaluation of the classifier \cite{DBLP:journals/ml/AbdulrahmanBRV18}. They call this combined measure of accuracy and time A3R, and integrate it into to different ranking approaches. In both cases, this lead to a better mean interval loss, which is a measure that expresses the mean loss experienced in respect to the time that has been allowed for the construction of the ranking.

@@

% Active testing A3R
The second approach does not initially use meta knowledge and is called active testing. Active testing is a strategy that 'intelligently select the most useful tests' \cite{DBLP:journals/ml/AbdulrahmanBRV18} to perform on a given data sets. Tests in this context mean the evaluation of a classifier that is considered for the ranking on the given data set. The authors aim to improve this strategy by reducing the time needed to identify a good algorithm by, similarly to the rank aggregation, incorporating time in the estimations made by the strategy which previously only compared accuracy values.
